What makes musicians infer teaching intentions?

### 2022-04-26 paper/manuscript.Rmd
update figures / manuscript except for general discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

abstract: |
  Perceiving pedagogical intentions is vital when learning skills from others. Here we investigated whether the modulations that expert pianists produce when they intend to teach are also perceived by listeners as conveying pedagogical intentions. Musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented. They were asked to judge whether each recording was produced for teaching purposes or not. The findings in Experiment 1 with a simple musical scale demonstrated that the accuracy of musicians' judgments was significantly above chance. Also, slower tempo contributed to musicians’ judgments as teaching regardless of the techniques. Moreover, performances with exaggeration for each technique were more likely to be judged as teaching. Experiment 2 aimed to replicate the findings of Experiment 1 with a more naturalistic piece. The accuracy of musicians' judgments was significantly above chance. However, we only replicated that performances with exaggerated dynamics were more likely to be judged as teaching. Taken together, loudness seems to be reliably used to infer teaching intentions regardless of the complexity of a musical piece. Also, typical pedagogical behaviour such as slowing down may not be necessarily perceived as teaching performance when learning complex skills such as artistic expression.

keywords          : "perception, expression, learning, expertise, music education"

@@

# Introduction
Learning from others is one of the important elements of skill acquisition. Not only are we able to learn by observing and imitating others, but also we benefit greatly from interacting with others such as teachers and peers [@tomasello_1993]. Adults are often being pedagogical to children in order to explain and transmit cultural conventions [@csibra_2009]. Active teaching seems to play a crucial role not only to transit skills over generations but also to further develop sophisticated cultures, which cannot be achieved by one single individual or generation [@tennie_2009]. From a learner's perspective, it is important to identify informative teachers and infer teachers' expectations so that learners can acquire skills through interacting with teachers [@gweon_2020; @veissiere_2020].

In pedagogical settings where teachers are supposed to convey useful information to learners, it has been found that teachers often modulate their behaviour for teaching purposes. For example, adults are likely to modulate their speech and action for infants so as to help infants acquire skills [e.g., @brand_2002; @saint-georges_2013]. Further studies have revealed that even towards adult learners, people modulate their speech and action in a similar way as they did for infants [@mcellin_2017; @uther_2007]. Moreover, @mcellin_2018 demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements). These findings suggest that experts modified their speech and action to send teaching intentions and that novices could successfully perceive the intentions.

Tominaga, Knoblich & Sebanz (*submitted*) extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression. We investigated whether and how expert pianists are able to communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing a larger contrast between forte and piano) when intending to teach the musical expressive techniques. Therefore, it seems that even in the domain of expertise, experts exhibit pedagogical behaviours to highlight crucial performance aspects for potential learners.

@@

In the present study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented. They were asked to judge whether each recording was produced for teaching purposes or not. Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings) whereas the other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings). First, we calculated the accuracy of participants’ judgments to examine whether they could distinguish teaching recordings from performing recordings. Furthermore, recordings were quantified with regard to tempo, articulation and dynamics. Using correlations and multiple regression analysis, we examined which modulations of performance were used to infer teaching intentions.

If performers' intentions are understood by learners with basic musical skills, they should be able to distinguish teaching recordings from performing recordings. Moreover, the same modulations of pedagogical performance parameters observed in our previous experiments such as slower demonstration and exaggerated performance, should be used to infer teaching intentions by the learners. In Experiment 1 learners listened to performances that followed simple musical scales. In Experiment 2 learners listened to performances of a more naturalistic piece of music in an attempt to replicate the findings from Experiment 1.

@@

There were two blocks and each block only included the recordings with one musical expressive technique of either articulation or dynamics. Each block consisted of four practice trials and 48 experimental trials. Each recording was evaluated only once in the experiment. All participants completed both blocks and the order of the blocks was counterbalanced across the participants. The order of the recordings was randomised within each block.

At the end of the experiment, participants filled in a questionnaire about their demographic information and experience in musical instruments.

@@

### Accuracy
First, we examined whether participants could accurately distinguish the stimuli chosen from the teaching condition in Tominaga et al., (*submitted*; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (*submitted*; Experiment 1) as performing. We compared how accurate participants were against the chance level (50%). The correct responses were either pressing the yes button when listening to the teaching recordings or pressing the no button when listening to the performing recordings. The incorrect responses were either pressing the yes button when listening to the performing recordings or pressing the no button when listening to the teaching recordings.

### Correlations and multiple regression
Stimuli were quantified regarding tempo (interonset intervals; IOIs), articulation (key-overlap time; KOT), dynamics (key velocity; KV) and dynamics contrast (key velocity difference; KV-Diff) only for 16th notes. Interonset intervals are time intervals between onsets of adjacent notes. Larger IOIs indicate slower tempo while smaller IOIs indicate faster tempo. Key-overlap time is the time overlap between two adjacent notes, namely the difference between the offset time of the current note and the onset time of the ensuing note [e.g., @bresin_2000]. Positive KOT values indicate legato styles whereas negative KOT values indicate staccato styles. Key velocity is obtained from MIDI data to describe how fast a performer hit the key. Larger KV values indicate forte styles while smaller KV values indicate piano styles. Additionally, we also measured dynamics contrast where one subcomponent of the technique moves to the other (e.g., from forte to piano, from staccato to legato) to illustrate how much dynamics contrast a performer made at transition points.

To investigate relationships between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as teaching (i.e., what percentage of participants responded as "yes"), we first performed separate correlation analyses for each performance feature. Second, we run multiple regression that included all four performance features to examine which predictor significantly contributed to participants' judgments as teaching. Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs. staccato, forte vs. piano), we created four separate models that included different parts of the piece. Each model considered only parts of the piece that comprised either legato, staccato, forte or piano. For articulation recordings, there were two models. The Legato model (*Figure \ref{fig:stim1}*, 1) considered only legato parts of the performances. We entered the legato parts of KOT and KV and KV-Diff or transition points from legato to staccato. The Staccato model (*Figure \ref{fig:stim1}*, 2) considered only staccato parts of the performances. We entered the staccato parts of KOT and KV and KV-Diff of transition points from staccato to legato. Similarly, there were two models for dynamics recordings. The Forte model (*Figure \ref{fig:stim1}*, 3) considered only forte parts of the performances for KV and KOT, and transition points from forte to piano for KV-Diff. The Piano model (*Figure \ref{fig:stim1}*, 4) considered only piano parts of the performances for KV and KOT, and transition points from piano to forte for KV-Diff. With regard to tempo (IOIs), there was only one value for each recording regardless of the subcomponents because tempo was consistent across the performance. Therefore, we entered the same tempo value for the Legato and Staccato models or the Forte and Piano models.

@@

## Accuracy
A one sample *t*-test was performed to compare the accuracy of participants' judgments against the chance level (50%). The mean percentage of correct answers [*M* = `r sprintf('%.1f', subset$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset$SD_Percent)`] was significantly higher than chance (*t*(`r ttest_all$parameter`) = `r sprintf('%.2f', ttest_all$statistic)`, *p* `r if(ttest_all$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', ttest_all$p.value)))}`, cohen's *d* = `r sprintf('%.2f', coheneff_all$effsize)`).

@@

## Correlations
### Tempo (IOIs)
Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_ioi_art$p.value)))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_ioi_dyn$p.value)))}`, *Figure \ref{fig:ioi-1}*). Participants tended to identify slower performances as teaching.

```{r ioi-1, include = FALSE}
cor_ioi_1 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", shape = "Skill", add = "reg.line", palette = "d3", add.params = list(fill = "lightgray"), conf.int = TRUE, xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + labs(color = "Technique", shape = "Technique") + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()

@@

```{r kot-1, include = FALSE}
kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_kot_1 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-250, 200, 100)) + coord_cartesian(xlim = c(-250, 200), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()

@@

```{r vel-1, include = FALSE}
vel_all$Subcomponent <- factor(vel_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_vel_1 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()

@@

```{r vel-diff-1, include = FALSE}
vel_diff_all$Subcomponent <- factor(vel_diff_all$Subcomponent, levels = c("LtoS", "StoL", "FtoP", "PtoF"))
cor_vel_diff_1 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-35, 55, 20)) + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()

@@

## Multiple regression
In order to further explore which feature of performance contributed the most to participants' judgments as teaching, multiple regression analyses were conducted. Statistical model assumptions were tested using the *performance* R package [@ludecke_2021]. Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs. staccato, forte vs. piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in *Data analysis* and *Figure \ref{fig:stim1}*).

@@

```{r plot-ioi-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:ioi-1}Experiment 1: Scatter plot showing the correlation between tempo feature (IOIs) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus. Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
img_cor_ioi_1
```

```{r plot-kot-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:kot-1}Experiment 1: Scatter plot showing the correlation between articulation feature (KOT) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus. Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
img_cor_kot_1
```

```{r plot-vel-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-1}Experiment 1: Scatter plot showing the correlation between dynamics feature (KV) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus. Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
img_cor_vel_1
```

```{r plot-vel-diff-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-diff-1}Experiment 1: Scatter plot showing the correlation between dynamics contrast feature (KV-Diff) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus. Each line indicates a regression line and the gray bands display the 95 percent confidence intervals."}
img_cor_vel_diff_1
```

@@

Experiment 1 investigated whether musicians could distinguish teaching recordings from performing recordings accurately and which features of piano performance made them infer teaching intentions. The results demonstrated that musicians could choose correct answers above chance. Also, it was found that the accuracy of participants' judgments was better for dynamics recordings than for articulation recordings. When it comes to how performance features contributed to participants' judments, performances with slower tempo were more likely to be judged as teaching by musicians regardless of which expressive technique was implemented in the piece. For articulation recordings, performances with longer legato and shorter staccato were tended to be judged as teaching. For dynamics recordings, performances with louder forte were more likely to be judged as teaching whereas there was no relationship between softer sound (i.e., piano) and participants' judgments as teaching. Importantly, performances with larger contrast between forte and piano for both directions (i.e., from forte to piano, from piano to forte) were more likely to be judged as teaching. This result may suggest that dynamics contrast might be reliably used to infer teaching intentions, rather than absolute dynamics values themselves. Moreover, multiple regression analyses implied that tempo feature was the strongest predictor of participants' judgments as teaching in general whereas there were specific predictors depending on which expressive technique was implemented in the piece. These performance features were overall consistent with what expert pianists did in our previous experiments for teaching purposes. Therefore, our findings suggest that musicians may rely on generic pedagogical behaviours (e.g., slower demonstration, exaggeration) to infer teaching intentions of expert pianists when listening to recorded performances.

@@

The aim of Experiment 2 was to replicate the findings in Experiment 1 with a more naturalistic piece of music. Given the findings in Experiment 1, we predicted that slower performance would be likely to be judged as teaching regardless of which expressive technique (i.e., articulation or dynamics) was implemented. Also performances with exaggerated articulation and dynamics (in particular, longer legato and shorter staccato, larger contrast between forte and piano) would be likely to be judged as teaching.

@@

## Correlations
### Tempo (IOIs)
Unlike Experiment 1, there was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$p.value)))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$p.value)))}`, *Figure \ref{fig:ioi-2}*). Participants tended to identify slower performances as teaching for dynamics recordings.

```{r ioi-2, include = FALSE}
cor_ioi_2 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", shape = "Skill", add = "reg.line", palette = "d3",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + labs(color = "Technique", shape = "Technique") + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()

@@

```{r kot-2, include = FALSE}
kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_kot_2 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", shape = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-300, 150, 100)) + coord_cartesian(xlim = c(-300, 150), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica") + scale_color_grey()

>>>>

abstract: |
  Perceiving pedagogical intentions is vital when learning skills from others. Here we investigated whether the modulations that expert pianists produce when they intend to teach are also perceived by listeners as conveying pedagogical intentions. Musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented. They were asked to judge whether each recording was produced for teaching purposes or not. The findings in Experiment 1 with a simple musical scale demonstrated that the accuracy of musicians' judgments was significantly above chance. Also, slower tempo contributed to musicians’ judgments as teaching regardless of the techniques. Moreover, performances with exaggeration for each technique were more likely to be judged as teaching. Experiment 2 aimed to replicate the findings of Experiment 1 with a more naturalistic piece. The accuracy of musicians' judgments was significantly above chance. In contrast to Experiment 1, only exaggerated dynamics were more likely to be judged as teaching. Taken together, the results indicate that recognition of some teaching intentions may be facilitated by low musical complexity.

keywords          : "perception, expression, pedagogy, expertise, music education"

@@

# Introduction
Learning from others is one of the important elements of skill acquisition. Not only are we able to learn by observing and imitating others, but also we benefit greatly from interacting with others such as teachers and peers [@tomasello_1993]. Adults are often being pedagogical to children to explain and transmit cultural conventions [@csibra_2009]. Active teaching seems to play a crucial role not only to transit skills over generations but also to further develop sophisticated cultures, which cannot be achieved by one single individual or generation [@tennie_2009]. From a learner's perspective, it is important to identify informative teachers and infer teachers' expectations so that learners can acquire skills through interacting with teachers [@gweon_2020; @veissiere_2020].

In pedagogical settings where teachers are supposed to convey useful information to learners, it has been found that teachers often modulate their behaviour for teaching purposes. For example, adults are likely to modulate their speech and action for infants to help them acquire skills [e.g., @brand_2002; @saint-georges_2013]. Further studies have revealed that even towards adult learners, people modulate their speech and action in a similar way as they did for infants [@mcellin_2017; @uther_2007]. Moreover, @mcellin_2018 demonstrated that people could identify informative intentions such as acting with others or teaching by relying on specific kinematics cues (e.g., velocity profiles of movements). These findings suggest that experts modified their speech and action to send teaching intentions and that novices could successfully perceive the intentions.

Tominaga, Knoblich & Sebanz (*submitted*) extended this line of research to expertise transmission where skills to be acquired are complex, such as when learning to perform with artistic expression. We investigated whether and how expert pianists communicatively modulate their performance when intending to teach the musical expressive techniques of articulation (the smoothness of sound) and dynamics (the loudness of sound). The results demonstrated that expert pianists systematically modulated their performance by playing slower or by exaggerating relevant aspects of the performance (e.g., producing shorter staccato or producing a larger contrast between forte and piano) when intending to teach musical expressive techniques. Therefore, it seems that experts exhibit pedagogical behaviours to highlight crucial performance aspects for potential learners.

@@

In the present study, musicians listened to piano recordings where a musical expressive technique of either articulation or dynamics was implemented. They were asked to judge whether each recording was produced for teaching purposes or not. Half of the recordings was produced when pianists were instructed to play as if they were teaching the designated musical technique in a lesson (i.e., teaching recordings). The other half was produced when pianists were instructed to play as if they were performing it in a concert (i.e., performing recordings). First, we calculated the accuracy of participants’ judgments to examine whether they could distinguish teaching recordings from performing recordings. Furthermore, recordings were quantified with regard to tempo, articulation and dynamics. Using correlations and multiple regression analysis, we examined which modulations of performance were used to infer teaching intentions.

If performers' intentions are understood by learners with basic musical skills, they should be able to distinguish teaching recordings from performing recordings. Moreover, the same modulations of pedagogical performance parameters observed in our previous experiments such as slower demonstration and exaggerated performance, should be used to infer teaching intentions by the learners. In Experiment 1 learners listened to performances that followed simple musical scales. In Experiment 2 learners listened to performances of a more complex piece.

@@

There were two blocks and each block only included the recordings with one musical expressive technique of either articulation or dynamics. Each block consisted of four practice trials and 48 experimental trials. Each recording was evaluated only once in the experiment. All participants completed both blocks. The order of the blocks was counterbalanced across participants. The order of the recordings was randomised within each block.

At the end of the experiment, participants filled in a questionnaire about their demographic information and thier prior experience with playing musical instruments.

@@

### Accuracy
First, we examined whether participants could accurately distinguish the stimuli chosen from the teaching condition in Tominaga et al., (*submitted*; Experiment 1) as teaching and the stimuli chosen from the performing condition in Tominaga et al., (*submitted*; Experiment 1) as performing. We compared how accurate participants were against the chance level (50%). Correct responses were either pressing the yes button when listening to teaching recordings or pressing the no button when listening to performing recordings. Incorrect responses were either pressing the yes button when listening to performing recordings or pressing the no button when listening to teaching recordings.

### Correlations and multiple regression
Stimuli were quantified regarding tempo (interonset intervals; IOIs), articulation (key-overlap time; KOT), dynamics (key velocity; KV) and dynamics contrast (key velocity difference; KV-Diff) only for 16th notes. Interonset intervals are time intervals between onsets of adjacent notes. Larger IOIs indicate slower tempo while smaller IOIs indicate faster tempo. Key-overlap time is the time overlap between two adjacent notes, namely the difference between the offset time of the current note and the onset time of the ensuing note [e.g., @bresin_2000]. Positive KOT values indicate a legato style whereas negative KOT values indicate a staccato style. Key velocity is obtained from MIDI data to describe how fast a performer hit the key. Larger KV values indicate a forte style while smaller KV values indicate a piano style. Additionally, we also measured dynamics contrast where one subcomponent of the technique moves to the other (e.g., from forte to piano, from staccato to legato) to illustrate how much dynamics contrast a performer made at transition points.

To investigate the relationships between performance features (i.e., IOIs, KOT, KV, KV-Diff) and participants' judgments as teaching (i.e., what percentage of participants responded as "yes"), we first performed separate correlation analyses for each performance feature. Second, we run multiple regression that included all four performance features to examine the strongest predictor of participants' judgments as teaching. Since articulation and dynamics were comprised of two opposite directional values (i.e., legato vs. staccato, forte vs. piano), we created four separate models that included different parts of the piece. Each model considered only parts of the piece that comprised either legato, staccato, forte or piano. For articulation recordings, there were two models. The Legato model (*Figure \ref{fig:stim1}*, 1) considered only legato parts of the performances. We entered the legato parts of KOT and KV and KV-Diff or transition points from legato to staccato. The Staccato model (*Figure \ref{fig:stim1}*, 2) considered only staccato parts of the performances. We entered the staccato parts of KOT and KV and KV-Diff of transition points from staccato to legato. Similarly, there were two models for dynamics recordings. The Forte model (*Figure \ref{fig:stim1}*, 3) considered only forte parts of the performances for KV and KOT, and transition points from forte to piano for KV-Diff. The Piano model (*Figure \ref{fig:stim1}*, 4) considered only piano parts of the performances for KV and KOT, and transition points from piano to forte for KV-Diff. With regard to tempo (IOIs), there was only one value for each recording regardless of the subcomponents because tempo was consistent across the performance. Therefore, we entered the same tempo value for the Legato and Staccato models or the Forte and Piano models.

@@

## Accuracy
A one sample *t*-test was performed to compare the accuracy of participants' judgments against chance level (50%). The mean percentage of correct answers [*M* = `r sprintf('%.1f', subset$Mean_Percent)`, *SD* = `r sprintf('%.2f', subset$SD_Percent)`] was significantly higher than chance (*t*(`r ttest_all$parameter`) = `r sprintf('%.2f', ttest_all$statistic)`, *p* `r if(ttest_all$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', ttest_all$p.value)))}`, cohen's *d* = `r sprintf('%.2f', coheneff_all$effsize)`).

@@

## Correlations
### Tempo (IOIs)
Performance tempi (IOIs) were significantly correlated with participants' judgments as teaching for both techniques (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_ioi_art$p.value)))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.3f', cor_ioi_dyn$p.value)))}`, *Figure \ref{fig:ioi-1}*). Participants identified slower performances as teaching.

```{r ioi-1, include = FALSE}
cor_ioi_1 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line", palette = "d3", add.params = list(fill = "lightgray"), conf.int = TRUE, xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + labs(color = "Technique", shape = "Technique") + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")

@@

```{r kot-1, include = FALSE}
kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_kot_1 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-250, 200, 100)) + coord_cartesian(xlim = c(-250, 200), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")

@@

```{r vel-1, include = FALSE}
vel_all$Subcomponent <- factor(vel_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_vel_1 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")

@@

```{r vel-diff-1, include = FALSE}
vel_diff_all$Subcomponent <- factor(vel_diff_all$Subcomponent, levels = c("LtoS", "StoL", "FtoP", "PtoF"))
cor_vel_diff_1 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-35, 55, 20)) + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")

@@

## Multiple regression
In order to further investigate which feature of performance contributed most to participants' judgments as teaching, multiple regression analyses were conducted. Statistical model assumptions were tested using the *performance* R package [@ludecke_2021]. Since articulation and dynamics consisted of two opposite subcomponents (i.e., legato vs. staccato, forte vs. piano) and therefore cannot be summed up to represent each technique as one value, we reported four separate regression models for each subcomponent (see details in *Data analysis* and *Figure \ref{fig:stim1}*).

@@

```{r plot-ioi-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:ioi-1}Experiment 1: Scatter plot showing the correlation between tempo feature (IOIs) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus. The gray bands display the 95 percent confidence intervals."}
img_cor_ioi_1
```

```{r plot-kot-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:kot-1}Experiment 1: Scatter plot showing the correlation between articulation feature (KOT) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus. The gray bands display the 95 percent confidence intervals."}
img_cor_kot_1
```

```{r plot-vel-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-1}Experiment 1: Scatter plot showing the correlation between dynamics feature (KV) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus. The gray bands display the 95 percent confidence intervals."}
img_cor_vel_1
```

```{r plot-vel-diff-1, fig.align = "center", out.width = "70%", fig.cap = "\\label{fig:vel-diff-1}Experiment 1: Scatter plot showing the correlation between dynamics contrast feature (KV-Diff) and average participants' judgments as teaching for each recording. Therefore, each dot represents each stimulus. The gray bands display the 95 percent confidence intervals."}
img_cor_vel_diff_1
```

@@

Experiment 1 investigated whether musicians could distinguish teaching recordings from performing recordings and which features of piano performance made them infer teaching intentions. The results demonstrated that musicians could choose correct answers above chance. Also, it was found that the accuracy of participants' judgments was better for dynamics recordings than for articulation recordings.

Performances with slower tempo were more likely to be judged as teaching by musicians regardless of which expressive technique was implemented in the piece. For articulation recordings, performances with longer legato and shorter staccato were tended to be judged as teaching. For dynamics recordings, louder performances were more likely to be judged as teaching whereas there was no relationship between softer sound and participants' judgments as teaching. Importantly, performances with larger contrast between forte and piano for both directions (i.e., from forte to piano, from piano to forte) were more likely to be judged as teaching. This result may suggest that dynamics contrast might be reliably used to infer teaching intentions, rather than absolute dynamics values themselves. Moreover, multiple regression analyses implied that tempo feature was the strongest predictor of participants' judgments as teaching in general whereas there were specific predictors depending on which expressive technique was implemented in the piece. These performance features were overall consistent with what expert pianists did in our previous experiments for teaching purposes. Therefore, our findings suggest that musicians may rely on generic pedagogical behaviours (e.g., slower demonstration, exaggeration) to infer teaching intentions of expert pianists when listening to recorded performances.

@@

The aim of Experiment 2 was to replicate the findings in Experiment 1 with a more complex piece of music. Given the findings in Experiment 1, we predicted that slower performance would be likely to be judged as teaching regardless of which expressive technique (i.e., articulation or dynamics) was implemented. Also performances with exaggerated articulation and dynamics (in particular, longer legato and shorter staccato, larger contrast between forte and piano) would be likely to be judged as teaching.

@@

## Correlations
### Tempo (IOIs)
There was a significant relationship between performance tempi (IOIs) and participants' judgments as teaching only for dynamics recordings (Articulation; *r(`r cor_ioi_art$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$estimate))`, *p* `r if(cor_ioi_art$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_art$p.value)))}`, Dynamics; *r(`r cor_ioi_dyn$parameter`)* = `r sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$estimate))`, *p* `r if(cor_ioi_dyn$p.value < 0.001){"< .001"} else {paste("= ", sub("^(-?)0.", "\\1.", sprintf('%.2f', cor_ioi_dyn$p.value)))}`, *Figure \ref{fig:ioi-2}*). Participants tended to identify slower performances as teaching for dynamics recordings.

```{r ioi-2, include = FALSE}
cor_ioi_2 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line", palette = "d3",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + labs(color = "Technique", shape = "Technique") + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")

@@

```{r kot-2, include = FALSE}
kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_kot_2 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-300, 150, 100)) + coord_cartesian(xlim = c(-300, 150), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")
